\documentclass[]{article}

\begin{document}

\title{Daily Meetings Multimedia Services Group 5}
\maketitle

\section*{May 22th}

\subsection*{Demo}
\begin{itemize}
	\item	Tomas is not present at the demo. 
	\item Random song, add some recommendation to the system so the users receives a valuable song. Since the user can explore our application with the 'Random' button, it should have more value than just selecting a random song from the collection.
	\item Elephant Candy; recommendation based on part of a mix
	\item Mistake with EAD on Blackboard, explain in mail how/what.
\end{itemize}

\subsection*{Daily Meeting}
\begin{itemize}
	\item Arthur; Split a mix into separate tracks with the waveformjs library
	\item Daan; Improve the user interface
	\item Jordy; Feature essentia
	\item Stefan; Helping with Arthur plus refactor of existing code for the midterm
	\item Tomas; ?
\end{itemize}

\section*{May 21th}
\subsection*{Daily Meeting}
\begin{itemize}
	\item Arthur; Route refactoring issue fixed
	\item Daan; Pull request TrackProcessor, feature essentia into database/parser will be skipped since it's not of use now, will be postponed. Will be working on UI
	\item Jordy;  Feature essentia, still no concrete progress, difficult to understand what to use
	\item Stefan; EAD, review of pull request (took some time), split of mix
	\item Tomas; Content filtering fully tested now, prepare for pull request
\end{itemize}

\section*{May 20th}
\subsection*{Daily Meeting}
\begin{itemize}
	\item Arthur; Refactoring plus mix splitter 
	\item Daan; Not present, given notice of this earlier this week
	\item Jordy; ?
	\item Stefan; Checkstyle done, will work on the mix splitter with Arthur
	\item Tomas; Been busy with algorithm selector. Comment filtering is probably next week done.
\end{itemize}

\section*{May 19th}
\subsection*{Daily Meeting}
\begin{itemize}
	\item Arthur; How to split a mix difficult, will be a combination of comments/description and feature essentia.
	\item Daan; Track parser is done. Track receiver next.
	\item Jordy; Log in/out done. Feature essentia next.
	\item Stefan; Random song has a pull request, working with Arthur on the mix splitter
	\item Tomas; fixing goodsnippet pr, making a start on the algorithm selector
\end{itemize}

\section*{May 18th}
\subsection*{Daily Meeting}
\begin{itemize}
	\item Arthur; Start mix splitter
	\item Daan; .track info parser will take longer than expected since there are newlines allowed in the titles
	\item Jordy; prepare Log in pr, need to show users collection after log in
	\item Stefan; Random song
	\item Tomas; Start with algorithm selector
\end{itemize}

\section*{May 13th}
\subsection*{Daily Meeting}
\begin{itemize}
	\item Arthur; Database name and url should be differently implemented, maybe via api. Widget reload needs refactor
	\item Daan; MySQL is now on a remote server, transferring the data. Next .track parser
	\item Jordy; Log in, extract user is done, next is to pass the users data.
	\item Stefan; Random song, query done and methods and test also. Waiting on mysql server
	\item Tomas; Correct comment class + test, need a fix for when a track has less than 3 comments. Check out April fools Soundcloud 'drop' feature.
\end{itemize}

\section*{Date}
\subsection*{Daily Meeting}
\begin{itemize}
	\item Arthur; 
	\item Daan; 
	\item Jordy; 
	\item Stefan; 
	\item Tomas; 
\end{itemize}

\end{document}